Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
rw A out
icpc19
pagebreak out; other small fixes
fix
fixed conflict
fixing sentence

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage[table,xcdraw]{xcolor}
\usepackage{framed}
\usepackage{float}
\usepackage{xcolor}

\usepackage{xfrac}

@@

	\item A replication package with all scripts and data created to perform the
	empirical evaluation, for reproducibility. Available here: $<url>$.

@@

\setcounter{lstannotation}{0}
\begin{lstlisting}[caption={Fix provided by OpenSSL developers to the
\\CVE-2014-3506 vulnerability},label={lst:vuln}]
+ static unsigned long dtls1_max_handshake_message_len(const SSL *s){ /*!\annotation{lst:func1}!*/
+  unsigned long max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;
+  if(max_len < (unsigned long)s->max_cert_list) /*!\annotation{lst:func2}!*/
+     return s->max_cert_list;
+  return max_len;
+ }

@@

\ref{lst:func2} Checks if the maximum certificate list size
(\texttt{s-$>$max\_cert\_list}) requires more length than the maximum length
(\texttt{max\_len}). If yes, it return the certificate list size, if not it
return the maximum length.

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.5\textwidth]{figures/language_dist.pdf}
 	\caption{Distribution of security refactorings per language}
	\label{fig:lang}
\end{figure}

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.50\textwidth]{figures/type_dist.pdf}
 	\caption{Distribution of project domain}
	\label{fig:domain}
\end{figure}

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.50\textwidth]{figures/bch_report.png}
 	\caption{Maintainability report of OpenSSL's CVE-2014-3506 vulnerability
refactoring for the guideline \emph{Write Simple Units of Code} provided by
\emph{Better Code Hub}. This version of OpenSSL does not comply with the
guideline in the example since the bars do not reach the threshold points. This
example only complies with $\sfrac{1}{10}$ guidelines (\emph{Write Clean Code}).}
	\label{fig:bchrep}
\end{figure}

@@

Many studies have investigated the relationship between refactorings and software quality.

\subsection{Software Maintainability}

Previous work focused on coupling metrics has evaluated the impact of refactorings and
exhibited proof that quantifying effectively the impact of refactoring on maintainability
may help to choose the appropriate refactoring type~\cite{1167822}. In contrast to
this work, Hegedus et al.~\cite{HEGEDUS2018313} did not select particular metrics to
assess the effect of refactorings. Instead, statistical tests were used to find
the metrics that have the potential to change significantly after refactorings.
The differences of maintainability between groups of refactored elements and
non-refactored were analyzed. And, the authors conclude that the source
code elements subjected to refactorings had significantly lower maintainability
than the elements not affected. Studying the evolution of maintaninability issues during the development of
Android apps, Malavolta et al. (2018)~\cite{8530041} discovered that maintainability
decreases over time. Palomba et al. (2018)\cite{Palomba:2018:DIM:3231288.3231337} exhibits
proof that code smells should be carefully monitored by programmers, since there is
a high correlation between maintainability aspects and proneness to changes and faults.
The present work is based on the 10 guidelines proposed
by the Software Improvement Group (SIG) and focuses solely on evaluating
the impact of patching vulnerabilities on software maintainability.

>>>>

\documentclass[10pt,conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{booktabs}
\usepackage[table,xcdraw]{xcolor}
\usepackage{framed}
\usepackage{float}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{xfrac}

@@

	\item A replication package with all scripts and data created to perform the
	empirical evaluation, for reproducibility. Available online:
  \url{https://figshare.com/s/3e17518222df6a11a8d6}.

@@

\medskip

\setcounter{lstannotation}{0}
\begin{lstlisting}[caption={Fix provided by OpenSSL developers to the
\\CVE-2014-3506 vulnerability},label={lst:vuln}]

+ static unsigned long dtls1_max_handshake_message_len(const SSL *s){ /*!\annotation{lst:func1}!*/
+  unsigned long max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;
+  if(max_len < (unsigned long)s->max_cert_list) /*!\annotation{lst:func2}!*/
+     return s->max_cert_list;
+  return max_len;
+ }

@@

\ref{lst:func2} Checks if the maximum certificate list size
(\texttt{s-$>$max\_cert\_list}) requires more length than the maximum length
(\texttt{max\_len}). If that condition holds, the function returns the size of
the certificate list, otherwise it returns the maximum length.

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.5\textwidth]{figures/language_dist.pdf}
 	\caption{Distribution of Security Refactorings per Language}
	\label{fig:lang}
\end{figure}

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.5\textwidth]{figures/type_dist.pdf}
 	\caption{Distribution of Projects Domain}
	\label{fig:domain}
\end{figure}

@@

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.5\textwidth]{figures/bch_report.png}
 	\caption{Maintainability report of OpenSSL's CVE-2014-3506 vulnerability
refactoring for the guideline \emph{Write Simple Units of Code} provided by
\emph{Better Code Hub}. This version of OpenSSL does not comply with the
guideline in the example since the bars do not reach the threshold points. This
example only complies with $\sfrac{1}{10}$ guidelines (\emph{Write Clean Code}).}
	\label{fig:bchrep}
\end{figure}

@@

Many studies have investigated the relationship between refactorings and software quality.
Previous work focused on coupling metrics has evaluated the impact of refactorings and
exhibited proof that quantifying effectively the impact of refactoring on maintainability
may help to choose the appropriate refactoring type~\cite{1167822}. In contrast to
this work, Hegedus et al.~\cite{HEGEDUS2018313} did not select particular metrics to
assess the effect of refactorings. Instead, statistical tests were used to find
the metrics that have the potential to change significantly after refactorings.
The differences of maintainability between groups of refactored elements and
non-refactored were analyzed. And, the authors conclude that the source
code elements subjected to refactorings had significantly lower maintainability
than the elements not affected. Studying the evolution of maintaninability issues during the development of Android apps, Malavolta et al. (2018)~\cite{8530041} discovered that maintainability
decreases over time. Palomba et al. (2018)\cite{Palomba:2018:DIM:3231288.3231337} exhibits
proof that code smells should be carefully monitored by programmers, since there is
a high correlation between maintainability aspects and proneness to changes and faults.
The present work is based on the 10 guidelines proposed
by the Software Improvement Group (SIG) and focuses solely on evaluating
the impact of patching vulnerabilities on software maintainability.
